### 2021-05-13 shared/analysis.tex
WIP : Optimization

\begin{equation}	
	w_1 = \prod_{j=1}^{10} choice\_prob_{1}(j) ,
	\quad
	sum_1 = \sum_{j=1}^{10} components(\vec{d_1}) ,
\end{equation}
\begin{equation}	
	w_2 = \prod_{j=1}^{10} choice\_prob_{2}(j) ,
	\quad
	sum_2 = \sum_{j=1}^{10} components(\vec{d_2}) ,
\end{equation}
\begin{equation}	
	w_3 = \prod_{j=1}^{10} choice\_prob_{3}(j) ,
	\quad
	sum_3 = \sum_{j=1}^{10} components(\vec{d_3}) ,
\end{equation}
\begin{equation}	
	w_4 = \prod_{j=1}^{10} choice\_prob_{4}(j) ,
	\quad
	sum_4 = \sum_{j=1}^{10} components(\vec{d_4}) ,
\end{equation}
\begin{equation}	
	w_5 = \prod_{j=1}^{10} choice\_prob_{5}(j) ,
	\quad
	sum_5 = \sum_{j=1}^{10} components(\vec{d_5}) ,
\end{equation}
\begin{equation}
	\vec{d_1} \neq \vec{d_2} \neq \vec{d_3} \neq \vec{d_4} \neq \vec{d_5}
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
\end{equation}
\begin{equation}
	\enspace
	EV(heads) = (w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\begin{equation}
	\enspace
	Objective_2 = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
Statistically, maximizing $Objective_1$ must also maximize $Objective_2$ and thus we make the query $maximize(\sum_{i=1}^{k}{w_i})$ to the optimizing solver finally.

\begin{figure}
	\centering
	\includegraphics[scale=0.15]{abstract.pdf}
	\caption{Multiple $random$ paths corresponding to different $\vec{d}$'s but a single $abstract$ path.}
\end{figure}

\begin{figure}
	\begin{minted}{python}
	prob = 0.435, n = 8 (8 coin flips), k = 240 (randomized paths)
	prob = 0.551, n = 5 (5 coin flips), k = 27 (randomized paths) 
	\end{minted}
	\caption{Values for \texttt{Assert} failure.}
\end{figure}
\end{document}

>>>>

\begin{equation}	
	w_1 = \prod_{j=1}^{10} choice\_prob_{1}(j) ,
	\quad
	sum_1 = \sum_{j=1}^{10} components(\vec{d_1}) ,
\end{equation}
\begin{equation}	
	w_2 = \prod_{j=1}^{10} choice\_prob_{2}(j) ,
	\quad
	sum_2 = \sum_{j=1}^{10} components(\vec{d_2}) ,
\end{equation}
\begin{equation}	
	w_3 = \prod_{j=1}^{10} choice\_prob_{3}(j) ,
	\quad
	sum_3 = \sum_{j=1}^{10} components(\vec{d_3}) ,
\end{equation}
\begin{equation}	
	w_4 = \prod_{j=1}^{10} choice\_prob_{4}(j) ,
	\quad
	sum_4 = \sum_{j=1}^{10} components(\vec{d_4}) ,
\end{equation}
\begin{equation}	
	w_5 = \prod_{j=1}^{10} choice\_prob_{5}(j) ,
	\quad
	sum_5 = \sum_{j=1}^{10} components(\vec{d_5}) ,
\end{equation}
\begin{equation}
	\vec{d_1} \neq \vec{d_2} \neq \vec{d_3} \neq \vec{d_4} \neq \vec{d_5}
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
\end{equation}
\begin{equation}
	\enspace
	EV(heads) = (w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\begin{equation}
	\enspace
	Objective_2 = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
We can make multiple optimization $objectives$ be fulfilled in one query, but the best results are produced for the $Objective_2$ since it minimizes the $error$ most.

\begin{equation}
	Obj_{1} = maximize(\sum_{i=1}^{k}{w_i * x _i}) \quad \mid \quad
	Obj_{2} = minimize(n * prob - \sum_{i=1}^{k}{w_i * x_i})
\end{equation}

\begin{figure}
	\centering
	\includegraphics[scale=0.16]{abstract.pdf}
	\caption{Multiple $random$ paths corresponding to different $\vec{d}$'s but a single $abstract$ path.}
\end{figure}

\begin{figure}
	\begin{minted}{python}
	prob = 0.435, n = 8 (8 coin flips), k = 240 (randomized paths)
	prob = 0.551, n = 5 (5 coin flips), k = 27 (randomized paths) 
	\end{minted}
	\caption{Values for \texttt{Assert} failure.}
\end{figure}

\end{document}
